Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}

### 2023-02-21 draft/draft.Rmd
lots of updates: draft, regressions, and new cleaning for wind

# Table
yieldtablehet[1,5] <- "0.000"
colnames(yieldtablehet) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablehet, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the *maximum* observed exposure. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(15), hline_after = TRUE) %>%
  row_spec(c(13), bold = TRUE) %>%
  add_header_above(c(" ", ">p(50)" = 1, "<=p(50)" = 1, "all" = 3)) %>%
  kable_classic_2()

@@

kable(
      labortablerural, caption = "Wind direction and labor allocation, rural only",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(5,10), hline_after = TRUE) %>%
  row_spec(c(1,6,12), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(ntltable) <- c("(1)", "(2)", "(3)", "(4)")
kable(
      ntltable, caption = "Wind direction and nightlight growth",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is logged nightlights. Rainfall is included in columns (2) and (4). * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(c(9), hline_after = TRUE) %>%
  row_spec(c(5,8), bold = TRUE) %>%
  kable_classic_2()

>>>>

# Table
colnames(yieldtablehet) <- c(">p(50)", "<=p(50)", ">p(50)", "<=p(50)", "")
yieldtablehet[7:8,] <- "Yes"
kable(
      yieldtablehet, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the *maximum* observed exposure. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(6), bold = TRUE) %>%
  add_header_above(c(" ", "exposure" = 2, "yield" = 2, " " = 1)) %>%
  kable_classic_2()

@@

kable(
      labortablerural, caption = "Wind direction and labor allocation, by location",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(5,10), hline_after = TRUE) %>%
  row_spec(c(1,6,12), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(ntltable) <- c("(1)", "(2)", "(3)", "(4)")
newrow <- matrix(c("no", "yes", "no", "yes"), nrow = 1)
colnames(newrow) <- c("(1)", "(2)", "(3)", "(4)")
rownames(newrow) <- "weather"
ntltable <- rbind(ntltable[1:4,], newrow, ntltable[5:nrow(ntltable),])
kable(
      ntltable, caption = "Wind direction and nightlight growth",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is logged nightlights. Rainfall is included in columns (2) and (4). * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(c(10), hline_after = TRUE) %>%
  row_spec(c(6,9), bold = TRUE) %>%
  kable_classic_2()

### 2023-02-21 draft/draft.tex
lots of updates: draft, regressions, and new cleaning for wind

\title{Pollution, agricultural productivity, and development: Evidence from coal plants in India\footnote{I thank Marc Bellemare and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-02-10}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{>p(50)} & \multicolumn{1}{c}{<=p(50)} & \multicolumn{3}{c}{all} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.033*** & -0.004*** & 0.0006 & 0.000\\
 & (0.0002) & (0.002) & (0.0003) & (0.0005) & (0.001)\\
rain (z) & 0.028*** & 0.032*** & 0.028*** & 0.028*** & 0.028***\\
 & (0.0006) & (0.0005) & (0.0004) & (0.0004) & (0.0004)\\
mean temp (10s) & -0.001*** & 0.0006*** & -0.0004*** & -0.0004*** & -0.0004***\\
 & (7.66e-5) & (7.9e-5) & (5.55e-5) & (5.56e-5) & (5.49e-5)\\
wind x rain &  &  & 0.0005*** &  & \\
 &  &  & (6.74e-5) &  & \\
wind squared &  &  &  & -0.0002*** & \\
 &  &  &  & (3.58e-5) & \\
wind x starting yield &  &  &  &  & -0.001**\\
 &  &  &  &  & (0.0006)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,112,082 & 1,259,139 & 2,371,221 & 2,371,221 & 2,367,248\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the *maximum* observed exposure. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortablerural}Wind direction and labor allocation, rural only}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & all & all & self & wage & farm & non-farm\\
\midrule
\textbf{rural} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.112*** & -0.118*** & -0.050* & -0.068** & -0.002 & -0.116***\\
 & (0.036) & (0.029) & (0.030) & (0.031) & (0.028) & (0.034)\\
DV mean & 3.499 & 3.499 & 2.172 & 1.327 & 1.260 & 2.240\\
observations & 529,562 & 529,466 & 529,466 & 529,466 & 529,466 & 529,466\\
\midrule
\textbf{urban} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.020 & -0.030 & -0.011 & -0.019 & 0.023* & -0.053\\
 & (0.033) & (0.041) & (0.039) & (0.031) & (0.014) & (0.048)\\
DV mean & 3.040 & 3.040 & 1.393 & 1.647 & 0.101 & 2.939\\
observations & 369,483 & 369,390 & 369,390 & 369,390 & 369,390 & 369,390\\
\midrule
controls & No & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes & Yes & Yes & Yes\\
state-month & Yes & Yes & Yes & Yes & Yes & Yes\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:ntltable}Wind direction and nightlight growth}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind (lag) & -0.024*** & -0.024*** &  & \\
 & (0.003) & (0.003) &  & \\
wind (lead) &  &  & -0.001 & -0.001\\
 &  &  & (0.002) & (0.002)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\textbf{varying slopes:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
year (by village) & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,694,535 & 1,694,535 & 1,807,504 & 1,807,504\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is logged nightlights. Rainfall is included in columns (2) and (4). * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\title{Pollution, agricultural productivity, and development: Evidence from coal plants in India\footnote{I thank Marc Bellemare and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-02-11}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{exposure} & \multicolumn{2}{c}{yield} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & >p(50) & <=p(50) & >p(50) & <=p(50) & \\
\midrule
pm & -0.074*** & -0.012*** & -0.006*** & -0.066*** & -0.021***\\
 & (0.004) & (0.002) & (0.001) & (0.006) & (0.001)\\
pm (10s) times rain &  &  &  &  & 0.005***\\
 &  &  &  &  & (0.000)\\
weather & yes & yes & yes & yes & yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\midrule
observations & 650,770 & 1,720,451 & 1,192,644 & 1,178,577 & 2,371,221\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the *maximum* observed exposure. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortablerural}Wind direction and labor allocation, by location}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & all & all & self & wage & farm & non-farm\\
\midrule
\textbf{rural} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.112*** & -0.118*** & -0.050* & -0.068** & -0.002 & -0.116***\\
 & (0.036) & (0.029) & (0.030) & (0.031) & (0.028) & (0.034)\\
DV mean & 3.499 & 3.499 & 2.172 & 1.327 & 1.260 & 2.240\\
observations & 529,562 & 529,466 & 529,466 & 529,466 & 529,466 & 529,466\\
\midrule
\textbf{urban} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.020 & -0.030 & -0.011 & -0.019 & 0.023* & -0.053\\
 & (0.033) & (0.041) & (0.039) & (0.031) & (0.014) & (0.048)\\
DV mean & 3.040 & 3.040 & 1.393 & 1.647 & 0.101 & 2.939\\
observations & 369,483 & 369,390 & 369,390 & 369,390 & 369,390 & 369,390\\
\midrule
controls & No & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes & Yes & Yes & Yes\\
state-month & Yes & Yes & Yes & Yes & Yes & Yes\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:ntltable}Wind direction and nightlight growth}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind (lag) & -0.024*** & -0.024*** &  & \\
 & (0.003) & (0.003) &  & \\
wind (lead) &  &  & -0.001 & -0.001\\
 &  &  & (0.002) & (0.002)\\
weather & no & yes & no & yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\textbf{varying slopes:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
year (by village) & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,694,535 & 1,694,535 & 1,807,504 & 1,807,504\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is logged nightlights. Rainfall is included in columns (2) and (4). * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}
